### 2011-12-19 joint action and knowing others minds/interacting mindreaders.2.tex
small changes only

\begin{abstract}
***
\end{abstract}

@@

@@

Our aim in identifying the your-goal-is-my-goal is not to 
defend a detailed hypothesis about the mechanisms and processes involved in mindreading.
Instead our present concerns are limited to a normative question about the evidential basis of mindreading.
The your-goal-is-my-goal inference matters
not because it describes how interpreters actually assign goals
but because 
its existence reveals that interacting mindreaders can have access to evidence unavailable to those relying entirely on observation.

>>>>

\begin{abstract}
%Goal ascription is fundamental for mindreading.
What evidence grounds ascriptions of thoughts and actions,
and how does the evidence support the ascriptions?
In answering this question, 
philosophers sometimes ignore interaction and focus on mere observation.
The only evidence considered is 
evidence that would be available to mindreaders who observe their targets but are not necessarily in a position to interact with them.
The present paper identifies evidence 
that is available only to mindreaders capable of interacting with their targets.
Being poised to interact with others may enable one to know things about their minds which one might not otherwise be in a position to know.

%What evidence grounds ascriptions of goals to other agents' actions,
%and how does the evidence support the ascriptions?
%It is usually assumed that, in answering this question, 
%we can focus on observation and ignore interaction.
%We can restrict ourselves to evidence that would be available to mindreaders who observe their targets but are not necessarily in a position to interact with them.
%The present paper identifies evidence 
%which supports goal ascriptions
%and 
%is available only to mindreaders who are capable of interacting with their targets.

\end{abstract}

@@

***Goal ascription essential for verifying predictions of action.

@@

In principle,
exploiting your-goal-is-my-goal does not require that the interpreter actually be in a position to interact with her target.
It is sufficient (and would be necessary but for some special cases) that the target takes the interpreter to be in a position to interact with him. 
Our concern, however,
is with cases that are likely to be important for understanding
development or evolution (and ideally both).
This mandates a focus on interpreters of limited sophistication
who lack both deep insight into others' minds and fully-fledged communicative abilities.
Such interpreters are unlikely to be able to contrive or exploit situations in which they only appear to be in a position to interact with their targets.
So the explanatorily relevant cases are those 
in which an interpreter is manifestly in a position to interact with her target.

Our aim in identifying the your-goal-is-my-goal is not to 
defend a detailed hypothesis about the mechanisms and processes involved in mindreading.
Instead our present concerns are limited to a normative question about the evidential basis of mindreading.
The your-goal-is-my-goal inference matters
not because it describes how interpreters actually assign goals
but because 
its existence reveals that interacting mindreaders can have evidence that would be unavailable to them if they were relying   entirely on observation.%
